A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-05-19 04_Severity_MetaAnalysis.Rmd
add residual plots and intercept correction on back calculation

summary(PMsev_mvPer)

1- LaplacesDemon::invlogit(PMsev_mvPer$b)
mean(PM_dat_D[PM_dat_D$spray_management == "control","PM_final_severity"])
mean(PM_dat_D[PM_dat_D$spray_management == "Recommended_plus","PM_final_severity"])
```
This produces estimates which are too high and likely incorrect

>>>>

summary(PMsev_mvPer)
plot(rstandard(PMsev_mvPer)$z, ylim=c(-3,3), pch=19)

1- LaplacesDemon::invlogit(PMsev_mvPer$b + PMsev_mvPer$b[1])
mean(PM_dat_D[PM_dat_D$spray_management == "control","PM_final_severity"])
mean(PM_dat_D[PM_dat_D$spray_management == "Recommended_plus","PM_final_severity"])
```
This produces estimates which are too high and likely incorrect
